Enriching Object Detection with 2D-3D Registration and Continuous Viewpoint

### 2014-11-14 egpaper_final.tex
excised exps into tex file

\section{Experiments}

In this section, we validate our proposed NZ-WHO templates in two different ways. First, we make a set of NZ-WHO templates for a set of CAD models from various viewpoints. Then we run the bank of NZ-WHO templates as ensembles of weak detectors and show that the rendering image can be We want to see how robust the NZ-WHO to real images a

\subsection{Object Detection} 
Instance-level 2D-3D matching (registration) is a difficult problem since we need a CAD model that looks similar to the object in the image. Especially, due to extreme intraclass variability of chair \cite{Aubry14} used a very large collection of CAD models to cover variety of chairs. Similarly, \cite{Lim14}
Our ensemble of NZ-WHO templates is generated from rendering image with no calibration but shows strong performance on object detection. The baseline method are Aspect Layout Model (ALM) \cite{Xiang12} and VOC-DPM \cite{Pepik12}. Note that the baseline methods require complex 3D modeling and viewpoint annotated natural images.

The detection result is on Table \ref{tab:3dobject} and example output from our method is on Figure \ref{fig:3dobject}.

\begin{figure}[h]
    \begin{center}
    \setlength\tabcolsep{0pt}
\begin{tabular}{cc}
  \includegraphics[width=0.45\linewidth]{car_3dobject/7.png} &   
  \includegraphics[width=0.45\linewidth]{car_3dobject/8.png}\\ [-15pt]
%   (a) & (b) \\[0pt]
  \includegraphics[width=0.45\linewidth]{car_3dobject/11.png} &   
  \includegraphics[width=0.45\linewidth]{car_3dobject/12.png}\\ [-5pt]
%  (c) & (d) \\[0pt]
\end{tabular}
\end{center}
\caption{Detection results on 3D-Object dataset \cite{Savarese07}. Original image (left) and detection result overlaid on top with a bounding box and corresponding confidence score(right)}
  \label{fig:3dobject}
\end{figure}

% Also, we evaluated our method on PASCAL 2007 dataset.
% 
% \begin{table}[!htbp]
%   \begin{center}
%   \begin{tabular}{|c|c|c|c|c|}
%     \hline
%      AP &    Ours &    ELDA \cite{Hariharan12} & ESVM \cite{Malisiewicz11} & VOCDPM \cite{Pepik12} \\
%     \hline\hline
%     car      & 27.          &  38.4  & 40.1    &65.7  \\ 
%     bicycle  & 43.74 & 41      &  40.7   & 61.3   \\
%     \hline
%     \end{tabular}
%   \end{center}
%   \caption{Average Precision(AP) on PASCAL 2007 dataset. Though we do not need any training images and made templates in few minues, it performs on par with state of the art detector yet it gives high quality 2D-3D matching.}
%   \label{tab:pascal07}
% \end{table}

\subsection{Fine-Tuning and Viewpoint Estimation}

High performance object detectors usually generalizes very well. It can handle various intraclass variability, viewpoint change and occlusion. However due to this high generalization, sometimes it is very difficult to get accurate pose, category or 2D-3D matching. Our method, specialized in giving such accurate information, can be applied on any generic object detectors to give high quality metadata.

To show such ability, we evaluated our method on PASCAL 3D dataset \cite{Xiang14}. The dataset augments PASCAL 2012 images with high quality viewpoint annotations thus is ideal to measure pose estimation. The dataset proposes new metric called Average Viewpoint Precision (AVP) where it measures the area under viewpoint precision and detection recall curve. The viewpoints is measured by azimuth similarity. If the distance between predicted azimuth and ground truth azimuth is below a certain threshold, the viewpoint is correct. Note that the baseline methods (V-DPM, VOC-DPM) reported on the PASCAL 3D dataset are variants of DPM where each component of DPM account for various azimuths. Thus V-DPM and VOC-DPM provide discrete azimuth only whereas our method provides 3D viewpoint (yaw, pitch, roll), CAD instance (model index, rendering, depth) and focal length.

\begin{table*}[!htbp]
    \footnotesize
  \begin{center}
\begin{tabular}{|c|c|c|c|c|c|c|}
\hline
AP/AVP              & V-DPM \cite{Xiang14} & VOC-DPM \cite{Pepik12}  & \cite{Pepik12} + Ours (discrete) & \cite{Pepik12} + Ours (full) & R-CNN + Ours (discrete) & R-CNN + Ours (full)\\
\hline\hline
car-4v              & 37.2 / 20.2         & 45.6 / 36.9             & 47.6 / 42.7       & 47.6 / \textbf{42.7}        & 49.6 / 41.5         & 49.6 / 41.5\\ \hline
car-8v              & 37.3 / 23.5         & 47.6 / 36.6             & 47.6 / \textbf{39.8}       & 47.6 / 39.5        & 49.6 / 38.0         & 49.6 / 39.0\\ \hline
car-16v             & 36.6 / 18.1         & 46.0 / 29.6             & 47.6 / 32.7       & 47.6 / 33.0        & 49.6 / 34.0         & 49.6 / \textbf{34.3}\\ \hline
car-24v             & 36.3 / 13.7         & 42.1 / 24.6             & 47.6 / 27.4       & 47.6 / 27.4        & 49.6 / 27.0         & 49.6 / \textbf{27.6}\\ \hline
\hline
bicycle-4v          & 45.2 / 41.7         & 46.9 / 43.9             & 48.1 / 47.6       & 48.1 / 46.6        & 61.7 / 56.5         & 61.7 / \textbf{56.7}\\ \hline
bicycle-8v          & 47.3 / 36.7         & 48.1 / 40.3             & 48.1 / 40.6       & 48.1 / 40.6        & 61.7 / 48.9         & 61.7 / \textbf{49.2}\\ \hline
bicycle-16v         & 46.5 / 18.4         & 45.6 / 22.9             & 48.1 / 26.2       & 40.1 / 27.3        & 61.7 / 34.7         & 61.7 / \textbf{35.8}\\ \hline
bicycle-24v         & 44.4 / 14.3         & 45.9 / 16.7             & 48.1 / 21.5       & 40.1 / 20.9        & 61.7 / \textbf{27.0}         & 61.7 / 23.9\\ \hline
\end{tabular}
\end{center}
\caption{Average Precision(AP) and Average Viewpoint Precision(AVP) on PASCAL 3D dataset\cite{Xiang14}. For combined method (* + Ours), we use bounding boxes from * and augment viewpoint using our method. R-CNN and run our method to produce 2D-3D matching. If our method fails to give viewpoint, it predicts the viewpoint to be 0. Note that our method gives high quality metadata such as continuous 3D viewpoint, CAD model (rendering depth) and fine-grained category, whereas base-line methods gives 1D discrete azimuths. Our R-CNN was not an optimized version so the detection AP is lower than the state-of-the-art R-CNN performance}
\label{tab:pascal12}
\end{table*}

\subsection{Stability of Our Method for Irregular Bounding Boxes}

% Generic object detectors give overlapping detection bounding boxes of the same object which can be handled by non maximal suppression. For these overlapping detections,

R-CNN detection bounding boxes are irregular in shape since they come from other region proposal methods and sometimes they truncate objects. To handle such irregular shape and truncation, we added small context around the bounding boxes and run our method.

We assumed that object can be arbitrarily truncated by the bounding box and search all plausible scales and translations. This can be efficiently computed using FFT-based convolution (refer Section. \ref{sec:fft}). We put examples of such conditions in Figure \ref{fig:stability}. Although the input bounding boxes are irregular and truncate objects, our method reliably generated a reasonable prediction of pose, translation, scale and CAD model.

\begin{figure}[h]
\setlength\tabcolsep{5pt}
\begin{tabular}{cc}
  \includegraphics[width=0.45\linewidth]{car_pascal/1.png} &   
  \includegraphics[width=0.45\linewidth]{car_pascal/2.png} \\   
  \includegraphics[width=0.45\linewidth]{car_pascal/3.png} &   
  \includegraphics[width=0.45\linewidth]{car_pascal/4.png} \\   
\end{tabular}
\caption{Stability of our method for overlapping R-CNN detection \cite{Girshick14}. Blue box is the R-CNN detection that is feed into the system as initial detection. Purple box and overlaid rendering is the final output of the system. Note that for various overlapping bounding boxes, our system accurately estimated the reasonable result}
  \label{fig:stability}
\end{figure}

% For qualitative examples, we put hand-picked results from our method Fig. \ref{fig:car} and Fig. \ref{fig:bicycle}.

% \begin{figure*}[h]
% \setlength\tabcolsep{5pt}
% \begin{tabular}{|c|c|c|}
%     \hline
%   \includegraphics[width=0.325\textwidth]{car/PASCAL_car_val_init_0_Car_each_27_lim_250_lam_0_150_a_24_e_3_y_1_f_1_scale_2_00_sbin_6_level_15_skp_n_server_101_img_39.jpg} &   
%   \includegraphics[width=0.325\textwidth]{car/PASCAL_car_val_init_0_Car_each_27_lim_250_lam_0_150_a_24_e_3_y_1_f_1_scale_2_00_sbin_6_level_15_skp_n_server_101_img_78.jpg} & 
%   \includegraphics[width=0.325\textwidth]{car/PASCAL_car_val_init_0_Car_each_27_lim_250_lam_0_150_a_24_e_3_y_1_f_1_scale_2_00_sbin_6_level_15_skp_n_server_101_img_85.jpg} \\[-15pt]
% (a) & (b) & (c) \\[0pt]
% \hline
%   \includegraphics[width=0.325\textwidth]{car/PASCAL_car_val_init_0_Car_each_27_lim_250_lam_0_150_a_24_e_3_y_1_f_1_scale_2_00_sbin_6_level_15_skp_n_server_101_img_338.jpg} &   
%   \includegraphics[width=0.325\textwidth]{car/PASCAL_car_val_init_0_Car_each_27_lim_250_lam_0_150_a_24_e_3_y_1_f_1_scale_2_00_sbin_6_level_15_skp_n_server_101_img_360.jpg} & 
%   \includegraphics[width=0.325\textwidth]{car/PASCAL_car_val_init_0_Car_each_27_lim_250_lam_0_150_a_24_e_3_y_1_f_1_scale_2_00_sbin_6_level_15_skp_n_server_101_img_414.jpg} \\[-15pt]
% (d) & (e) & (f) \\[0pt]
% \hline
%   \includegraphics[width=0.325\textwidth]{car/PASCAL_car_val_init_0_Car_each_27_lim_250_lam_0_150_a_24_e_3_y_1_f_1_scale_2_00_sbin_6_level_15_skp_n_server_101_img_418.jpg} &   
%   \includegraphics[width=0.325\textwidth]{car/PASCAL_car_val_init_0_Car_each_27_lim_250_lam_0_150_a_24_e_3_y_1_f_1_scale_2_00_sbin_6_level_15_skp_n_server_101_img_1049.jpg} & 
%   \includegraphics[width=0.325\textwidth]{car/PASCAL_car_val_init_0_Car_each_27_lim_250_lam_0_150_a_24_e_3_y_1_f_1_scale_2_00_sbin_6_level_15_skp_n_server_101_img_1242.jpg} \\[-15pt]
% (g) & (h) & (i) \\[0pt]
% \hline
%   \includegraphics[width=0.325\textwidth]{car/PASCAL_car_val_init_0_Car_each_27_lim_250_lam_0_150_a_24_e_3_y_1_f_1_scale_2_00_sbin_6_level_15_skp_n_server_101_img_1244.jpg} &   
%   \includegraphics[width=0.325\textwidth]{car/PASCAL_car_val_init_0_Car_each_27_lim_250_lam_0_150_a_24_e_3_y_1_f_1_scale_2_00_sbin_6_level_15_skp_n_server_101_img_1261.jpg} & 
%   \includegraphics[width=0.325\textwidth]{car/PASCAL_car_val_init_0_Car_each_27_lim_250_lam_0_150_a_24_e_3_y_1_f_1_scale_2_00_sbin_6_level_15_skp_n_server_101_img_1452.jpg} \\[-15pt]
% (j) & (k) & (l) \\[0pt]
% \hline
%   \includegraphics[width=0.325\textwidth]{car/PASCAL_car_val_init_0_Car_each_27_lim_250_lam_0_150_a_24_e_3_y_1_f_1_scale_2_00_sbin_6_level_15_skp_n_server_101_img_1467.jpg} &   
%   \includegraphics[width=0.325\textwidth]{car/PASCAL_car_val_init_0_Car_each_27_lim_250_lam_0_150_a_24_e_3_y_1_f_1_scale_2_00_sbin_6_level_15_skp_n_server_101_img_1553.jpg} & 
%   \includegraphics[width=0.325\textwidth]{car/PASCAL_car_val_init_0_Car_each_27_lim_250_lam_0_150_a_24_e_3_y_1_f_1_scale_2_00_sbin_6_level_15_skp_n_server_101_img_1597.jpg} \\[-15pt]
% (m) & (n) & (o) \\[3pt]
% \hline
% \end{tabular}
%   \caption{Selected detections from PASCAL 07 Car categories. From the left, (1) original image, (2) overlaid true positive CAD models, (3) overlaid true positive CAD models with bounding boxes, (4) overlaid false positive CAD models with bounding boxes. Bounding box is colored from red (high confidence) to blue (low confidence) }
%   \label{fig:car}
% \end{figure*}
% \begin{figure*}[h]
% \setlength\tabcolsep{5pt}
% \begin{tabular}{|c|c|c|}
%     \hline
%   \includegraphics[width=0.325\textwidth]{bicycle/PASCAL_bicycle_val_init_0_Bicycle_each_4_lim_250_lam_0_150_a_48_e_4_y_5_f_1_scale_2_00_sbin_6_level_15_skp_n_server_102_img_459.jpg} &   
%   \includegraphics[width=0.325\textwidth]{bicycle/PASCAL_bicycle_val_init_0_Bicycle_each_4_lim_250_lam_0_150_a_48_e_4_y_5_f_1_scale_2_00_sbin_6_level_15_skp_n_server_102_img_1300.jpg} &   
%   \includegraphics[width=0.325\textwidth]{bicycle/PASCAL_bicycle_val_init_0_Bicycle_each_4_lim_250_lam_0_150_a_48_e_4_y_5_f_1_scale_2_00_sbin_6_level_15_skp_n_server_102_img_539.jpg} \\[-15pt]
% (a) & (b) & (c) \\[0pt]
% \hline
%   \includegraphics[width=0.325\textwidth]{bicycle/PASCAL_bicycle_val_init_0_Bicycle_each_4_lim_250_lam_0_150_a_48_e_4_y_5_f_1_scale_2_00_sbin_6_level_15_skp_n_server_102_img_35.jpg} &   
%   \includegraphics[width=0.325\textwidth]{bicycle/PASCAL_bicycle_val_init_0_Bicycle_each_4_lim_250_lam_0_150_a_48_e_4_y_5_f_1_scale_2_00_sbin_6_level_15_skp_n_server_102_img_83.jpg} &   
%   \includegraphics[width=0.325\textwidth]{bicycle/PASCAL_bicycle_val_init_0_Bicycle_each_4_lim_250_lam_0_150_a_48_e_4_y_5_f_1_scale_2_00_sbin_6_level_15_skp_n_server_102_img_131.jpg} \\[-15pt]
% (d) & (e) & (f) \\[0pt]
% \hline
%   \includegraphics[width=0.325\textwidth]{bicycle/PASCAL_bicycle_val_init_0_Bicycle_each_4_lim_250_lam_0_150_a_48_e_4_y_5_f_1_scale_2_00_sbin_6_level_15_skp_n_server_102_img_175.jpg} &   
%   \includegraphics[width=0.325\textwidth]{bicycle/PASCAL_bicycle_val_init_0_Bicycle_each_4_lim_250_lam_0_150_a_48_e_4_y_5_f_1_scale_2_00_sbin_6_level_15_skp_n_server_102_img_210.jpg} &   
%   \includegraphics[width=0.325\textwidth]{bicycle/PASCAL_bicycle_val_init_0_Bicycle_each_4_lim_250_lam_0_150_a_48_e_4_y_5_f_1_scale_2_00_sbin_6_level_15_skp_n_server_102_img_233.jpg} \\[-15pt]
% (g) & (h) & (i) \\[0pt]
% \hline
%   \includegraphics[width=0.325\textwidth]{bicycle/PASCAL_bicycle_val_init_0_Bicycle_each_4_lim_250_lam_0_150_a_48_e_4_y_5_f_1_scale_2_00_sbin_6_level_15_skp_n_server_102_img_322.jpg} &   
%   \includegraphics[width=0.325\textwidth]{bicycle/PASCAL_bicycle_val_init_0_Bicycle_each_4_lim_250_lam_0_150_a_48_e_4_y_5_f_1_scale_2_00_sbin_6_level_15_skp_n_server_102_img_348.jpg} &   
%   \includegraphics[width=0.325\textwidth]{bicycle/PASCAL_bicycle_val_init_0_Bicycle_each_4_lim_250_lam_0_150_a_48_e_4_y_5_f_1_scale_2_00_sbin_6_level_15_skp_n_server_102_img_375.jpg} \\[-15pt]
% (j) & (k) & (l) \\[0pt]
% \hline
%   \includegraphics[width=0.325\textwidth]{bicycle/PASCAL_bicycle_val_init_0_Bicycle_each_4_lim_250_lam_0_150_a_48_e_4_y_5_f_1_scale_2_00_sbin_6_level_15_skp_n_server_102_img_400.jpg} &   
%   \includegraphics[width=0.325\textwidth]{bicycle/PASCAL_bicycle_val_init_0_Bicycle_each_4_lim_250_lam_0_150_a_48_e_4_y_5_f_1_scale_2_00_sbin_6_level_15_skp_n_server_102_img_434.jpg} &   
%   \includegraphics[width=0.325\textwidth]{bicycle/PASCAL_bicycle_val_init_0_Bicycle_each_4_lim_250_lam_0_150_a_48_e_4_y_5_f_1_scale_2_00_sbin_6_level_15_skp_n_server_102_img_459.jpg} \\[-15pt]
% (m) & (n) & (o) \\[3pt]
% \hline
% \end{tabular}
%   \caption{Selected detections from PASCAL 12 Bike categories. From the left, (1) original image, (2) overlaid true positive CAD models, (3) overlaid true positive CAD models with bounding boxes, (4) overlaid false positive CAD models with bounding boxes. Bounding box is colored from red (high confidence) to blue (low confidence) }
%   \label{fig:bicycle}
% \end{figure*}

% \section{Object Detection with various Training Data}
% \section{Image Query}

>>>>

\section{Experiments}
\label{sec:experiments}
\input{experiments}
